% latex article template

% cheat sheet(eng): http://www.pvv.ntnu.no/~walle/latex/dokumentasjon/latexsheet.pdf
% cheat sheet2(eng): http://www.pvv.ntnu.no/~walle/latex/dokumentasjon/LaTeX-cheat-sheet.pdf
% reference manual(eng): http://ctan.uib.no/info/latex2e-help-texinfo/latex2e.html

% The document class defines the type of document. Presentation, article, letter, etc. 
\documentclass[12pt, a4paper]{article}

% packages to be used. needed to use images and such things. 
\usepackage[pdfborder=0 0 0]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\PassOptionsToPackage{hyphens}{url}

% hides the section numbering. 
\setcounter{secnumdepth}{-1}

% Graphics/image lications and extensions. 
\DeclareGraphicsExtensions{.pdf, .png, .jpg, .jpeg}
\graphicspath{{./images/}}

% Title or header for the document. 
\title{
TDT4280 - Exercise 4 \\
Distributed Problem Solving
}
% Author
\author{
		Jørgen Nordmoen \\
        Magnus L Kirø \\
}
\date{\today}

\begin{document}
\maketitle
\pagenumbering{arabic}

\section{Implementation}
description of the implementation. 

\section{Problem Decomposition}
2. Explain how you solved the task decomposition problem.

\section{Auctioin Type}
3. Explain which auction type you chose, and why. Advantages, disadvantages?

\section{Task Administration}
4. Describe the optimal strategy for the Task Administrator (see Section 8 above).

\section{Final Thoughts}
5. Summarize your final thoughts, problems encountered, lessons learned,etc.

6. Illustrate how your system decompose and solve tasks with an example.

(a) Describe what is done when, and which messages are sent to whom.

(b) Include a sequence diagram. (This can be automatically generated by JADE's Sniㄦ agent.) 
The diagram must include all relevant agents: at the very least the task administrator and all the solver agents.

\section{Jade start parameters}
7. List the parameters needed to start JADE with the GUI and enough instances of your agents.

\end{document}

