\section{An Optimal Strategy}\label{sec:optimal-strategy}
Our auction strategy is not optimal because of the general algorithm chosen, but
it could be extended to become something quite good. There of course would need
to be added some considerations to the algorithm to move it in the direction of
optimality. One of those is that the task administrator should consider the size
of each task before auctioning it. Estimating the time to solve and delegating
subproblems to other administrators would surely help it cope with larger, more
complex problems. There are many different suggestions for an optimal strategy
online and thus the one presented here will not be the absolute best, but it
should be a lot closer than what is currently implemented.

As mentioned above, a better performance will be gained when taking more complex
behaviors into consideration. To move in the direction of optimality the task
administrator should consider the size of the problem, if the problem instance
is small using a lot of time auctioning the problem will not gain that much. On
the other hand even if the problem instance is large a lot of auctions will
degrade performance because of the overhead of messages if the subproblems are
easy or quick to calculate. Load balancing is also an important consideration
which also present the need for more task administrators which should auction to
different solver agents. This also means that the top administrator need to
consider load balancing between its sub administrators. If we know noting more
about the underlying problem than its timing estimate the administrator will be
wholly dependant on the estimates reported and need to "test the water" so to
say in order to generate plans which it will use next time it encounters a
similar problem. To "test the waters" it needs to record the estimated time, the
solved time, the number of auctions and the time taken to auction, using this
data it could generate plans for what it should do next. 

This is all just expected to perform better, but is not necessarily going to
perform better because of the complexity. An optimal strategy then needs to take
all these concerns into consideration.
